Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
adjusted the social factors list

\begin{itemize}
\item Repositories: number of repositories the developer can access, including those
the developer owns, contributes
to, and for which the developer has organizational membership access.%
\footnote{https://developer.github.com/v3/repos/}
\item Stars: a count of the projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that follow the author. 
\item Following: number of developers that the author follows 
\item Contributions in the last year: number of contributions made by the author in the last year.
\end{itemize}

>>>>

\begin{itemize}
\item Number of repositories the developer can access, including those
the developer owns, contributes
to, and for which the developer has organizational membership access.%
\footnote{https://developer.github.com/v3/repos/}
\item  Number of projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Number of developers that follow the author. 
\item Number of developers that the author follows .
\item Number of contributions made by the author in the last year.
\end{itemize}
